---
title: "Analyze and Visualize Cheese Data with Shiny"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analyze and Visualize Cheese Data with Shiny}
  %\VignetteEngine{knitr::rmarkdown}
---



# Introduction

This vignette demonstrates the usage of three functions designed for analyzing and visualizing cheese data:
1. **Data cleaning**: The `clean_cheese_data()` function is used for cleaning the raw cheese data.
2. **Analysis functions**: The `analyze_fat_by_country()` function provides analytical tools for summarizing and visualizing cheese characteristics.
3. **Shiny app launcher**: The `launch_cheese_app()` function launches an interactive Shiny app for a more in-depth exploration of the cheese data.

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
# Load the functions (use relative paths)
source("/Users/wangshu/Desktop/assignment-4-packages-and-shiny-apps-shuwang0405/global.cheese.analysis/R/data_cleaning.R")
source("/Users/wangshu/Desktop/assignment-4-packages-and-shiny-apps-shuwang0405/global.cheese.analysis/R/analysis_functions.R")
source("/Users/wangshu/Desktop/assignment-4-packages-and-shiny-apps-shuwang0405/global.cheese.analysis/R/launch_app.R")


# Load necessary libraries
library(dplyr)
library(stringr)
library(tidyverse)
```

## Data Cleaning

### Example: Clean Raw Cheese Data

The `clean_cheese_data()` function handles missing values, converts fat content to numeric format, and standardizes country names.

```{r data-cleaning}
# Load raw cheese data
cheese_raw <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-06-04/cheeses.csv')

# Clean the data using the custom function
cheese_data_clean <- clean_cheese_data(cheese_raw)
head(cheese_data_clean)
```

## Analyze Fat Content by Country

The `analyze_fat_by_country()` function calculates the average fat content of cheese by country.

```{r avg-fat-country}
# Calculate average fat content by country
avg_fat_by_country <- analyze_fat_by_country(cheese_data_clean)
print(head(avg_fat_by_country, 10))
```

## Launch the Shiny App

The `launch_cheese_app()` function launches a Shiny app for interactive data exploration.

```{r, eval = FALSE}
# Launch the Shiny app (this command is not run in the vignette)
launch_cheese_app()
```

