---
title: "Analyze and Visualize Cheese Data with Shiny"
output: rmarkdown::html_vignette
---

# Introduction

This vignette demonstrates the usage of three functions designed for analyzing and visualizing cheese data:
1. **Data cleaning**: `data_cleaning.R` is used for cleaning the raw cheese data.
2. **Analysis functions**: `analysis_functions.R` provides analytical tools for summarizing and visualizing cheese characteristics.
3. **Shiny app launcher**: `launch_app.R` launches an interactive Shiny app for a more in-depth exploration of the cheese data.

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
# Load the functions
source("data_cleaning.R")
source("analysis_functions.R")
source("launch_app.R")
```

## Data Cleaning

### Example 1: Clean Raw Cheese Data

The `data_cleaning.R` script provides functions to clean the raw cheese dataset by handling missing values, converting data types, and standardizing text.

```{r data-cleaning}
# Load raw cheese data
cheese_raw <- read.csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-06-04/cheeses.csv')

# Clean the data using the custom function from data_cleaning.R
cheese_data_clean <- clean_cheese_data(cheese_raw)
head(cheese_data_clean)

```

**Explanation:** This function removes missing values, converts the fat content to numeric, and standardizes the country names to ensure consistent analysis.

## Analysis Functions

The `analysis_functions.R` script includes functions for summarizing and visualizing cheese characteristics, such as fat content and texture.

### Example 1: Average Fat Content by Country

```{r avg-fat-country}
# Calculate average fat content by country
avg_fat_by_country <- avg_fat_content_by_country(cheese_data_clean)
print(head(avg_fat_by_country, 10))
```

**Explanation:** This function calculates the average fat content for each country and returns a sorted list of the top countries with the highest average fat content.

### Example 2: Average Fat Content by Texture

```{r avg-fat-texture}
# Calculate average fat content by texture
avg_fat_by_texture <- avg_fat_content_by_texture(cheese_data_clean)
print(head(avg_fat_by_texture, 10))

```

**Explanation:** This function computes the average fat content for different cheese textures, highlighting how texture influences fat levels.

### Example 3: Visualize Fat Content

```{r plot-fat-content}
# Plot average fat content by country
plot_avg_fat_by_country(avg_fat_by_country)
```

**Explanation:** This visualization function displays a bar chart of the average fat content for the top countries, offering a quick view of regional cheese characteristics.

## Launching the Shiny App

The `launch_app.R` script contains the `launch_cheese_app()` function, which starts an interactive Shiny app to explore the cheese data further.

### Example: Launch the Shiny App

```{r launch-app, eval=FALSE}
# Launch the interactive Shiny app
launch_cheese_app()

```

**Explanation:** This command launches a Shiny app that allows users to interact with the cheese data, filter by country or texture, and visualize fat content dynamically.

## Conclusion

This vignette provides an overview of the three main scripts in the project: data cleaning, analysis, and interactive visualization. Together, these tools offer a comprehensive approach to exploring cheese characteristics, helping users better understand global cheese trends.

```

